quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-25 paper-quollr.Rmd
Updated Figure 6 title
Updated some figure captions

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="`detourr` output of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. These views illustrate how the lifted wireframe model captures the structure of the Scurve data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

@@

```{r tsne-link-limb, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout b (left) and the fitted model overlaid with the limb muscle data in $10\\text{-}D$ (right). Each color represents a different muscle group, with triangulated hexagon centroids on the NLDR layout connected to their corresponding regions in the high-dimensional projection using `langevitour`. Brushing in either view highlights the same subset of points across both panels, enabling exploration of how clusters in the low-dimensional embedding align with structures in the original high-dimensional space. Double-clicking clears the selection and removes highlights.", layout = "l-page"}

@@

```{r tsne-link-limb-best, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout f (left) and the fitted model overlaid with the limb muscle data in $10\\text{-}D$ (right). Each color represents a different muscle group, with triangulated hexagon centroids on the NLDR layout connected to their corresponding regions in the high-dimensional projection using `langevitour`. Brushing in either view highlights the same subset of points across both panels, enabling exploration of how clusters in the low-dimensional embedding align with structures in the original high-dimensional space. Double-clicking clears the selection and removes highlights.", layout = "l-page"}

>>>>

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="`detourr` output of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. These views illustrate how the lifted wireframe model captures the structure of the Scurve data. Regions with sparse or no data in the UMAP layout are also visible in the lifted model."}

@@

```{r tsne-link-limb, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the layout b (left) and the fitted model overlaid with the limb muscle data in $10\\text{-}D$ (right). Each color represents a different muscle group, with triangulated hexagon centroids on the NLDR layout connected to their corresponding regions in the high-dimensional projection using `langevitour`. Brushing in either view highlights the same subset of points across both panels, enabling exploration of how clusters in the low-dimensional embedding align with structures in the original high-dimensional space. Double-clicking clears the selection and removes highlights.", layout = "l-page"}

@@

```{r tsne-link-limb-best, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the layout f (left) and the fitted model overlaid with the limb muscle data in $10\\text{-}D$ (right). Each color represents a different muscle group, with triangulated hexagon centroids on the NLDR layout connected to their corresponding regions in the high-dimensional projection using `langevitour`. Brushing in either view highlights the same subset of points across both panels, enabling exploration of how clusters in the low-dimensional embedding align with structures in the original high-dimensional space. Double-clicking clears the selection and removes highlights.", layout = "l-page"}
